An umbrella review of the benefits and risks associated with youths' interactions with electronic screens

### 2023-06-21 reports/manuscript.tex
WIP: Fixing plots

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{\newline\indent Word count: 5369}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

The most frequently reported exposures were physically active video games (\emph{n} = 31), general screen use (\emph{n} = 27), general TV programs and movies (\emph{n} = 20), and screen-based interventions to promote health (\emph{n} = 14).
Supplementary File 1 provides a list of all exposures identified.
The most frequently reported outcomes were body composition (\emph{n} = 30), general learning (\emph{n} = 24), depression (\emph{n} = 13), and general literacy (\emph{n} = 12).
Of the 273 unique exposure/outcome combinations, 241 occurred in only one review, with 23 appearing twice, and 9 appearing three or more times.
Full characteristics of the included studies are provided in Supplementary File 2.
After removing reviews with duplicate exposure/outcome combinations, our process yielded 252 unique effect/outcome combinations (retaining multiple effects for different age groups or study designs) contributed from 102 reviews.
These effects represent the findings of 2,451 primary studies, involving 1,937,501 participants.
The characteristics of the included effects are available in Supplementary File 3.

@@

We identified 163 unique outcome-exposure combinations associated with health or health-related behaviour outcomes.
We removed 39 effects that did not provide individual study-level data, 50 effects with samples \textless{} 1,000, and 53 effects with a significant Egger's test or insufficient studies to conduct the test.
No remaining studies showed evidence of excessive significance.
Effects not meeting one or more of these standards are presented in Supplementary File 5.
The remaining 21 meta-analytic associations met our criteria for credible evidence and are described below (see also Figure 3).
These 21 effects came from 15 meta-analytic reviews analysing data from 344 empirical studies with 859,562 individual participants.

@@

As an example, consider children watching television programs---an often cited form of screen use harm.
We found statistically robust evidence for a small association with poorer academic performance and literacy skills for general television watching\textsuperscript{27}.
However, we also found evidence that if the content of the program was educational, or the child was watching the program with a parent (i.e., co-viewing), this exposure was instead associated with better literacy.\textsuperscript{28}
Thus, parents may play an important role in selecting content that is likely to benefit their children or, perhaps, interact with their children in ways that may foster literacy (e.g., asking their children questions about the program).
Similar nuanced findings were observed for video games.
The credible evidence we identified showed that video game playing was associated with poorer body composition and learning.\textsuperscript{27,29}
However, when the video game were designed specifically to teach numeracy, playing these games showed learning benefits.\textsuperscript{30}
One might expect that video games designed to be physically active could confer health benefits, but none of the meta-analyses examining this hypothesis met our thresholds for statistical credibility (see Supplementary Files 4 \& 5) therefore this hypothesis could not be addressed.

@@

Largely owing to a small number of studies or missing individual study data, there were few age-based conclusions that could be drawn from reviews which met our criteria for statistical certainty.
If we expand to include those reviews which did not meet this threshold, there remained no clear pattern although there were some age-specific differences in associations (data available in Supplementary Files 4 \& 5).
For example, advertising of unhealthy food was associated with unhealthy food choice for young children, but was not statistically significant for other age groups.\textsuperscript{36}
Conversely, TV programs and movies were more strongly associated with lower physical activity for adolescents than for younger age groups.\textsuperscript{37}
Given the differences in development across childhood and adolescence and the different ways children of various ages use screens, further examination of age-based differences is needed.
However, in the absence of this work, our study has shown how children are affected by screens in general.

@@

Our results have several implications for policy and practice.
Broadly, our findings align with the recommendations of others who suggest that current guidelines may be too simplistic, mischaracterise the strength of the evidence, or do not acknowledge the important nuances of the issue.\textsuperscript{38--40}
Our findings suggest that screen use is a complex issue, with associations based not just on duration and device type, but also on the content and the environment in which the exposure occurs.
Many current guidelines simplify this complex relationship as something that should be minimised.\textsuperscript{12,13}
We suggest that future guidelines need to embrace the complexity of the issue, to give parents and clinicians specific information to weigh the pros and cons of interactions with screens.

Given our results, we support the continuing trend of guidelines moving away from recommendations to reduce `screen use', and instead focusing on the type of screen use.
For example, we suggest that guidelines should discourage high levels of social media and internet use.
Guidelines may also consider adapting recommendations that promote the use of educational apps and video games, although these recommendations need to be balanced against the (very small) risks to adiposity.\textsuperscript{41}

Our results also have implications for future research.
Screen use research is extensive, varied, and rapidly growing.
Reviews tended to be general (e.g., all screen use) and even when more targeted (e.g., social media) nuances related to specific content (e.g., Instagram vs Facebook) have not been meta-analysed or have not produced credible evidence.
Fewer than 20\% of the effects identified met our criteria for statistical credibility.
Most studies which did not meet our criteria failed to provide study-level data (or did not provide sufficient data, such as including effect estimates but not sample sizes).
Newer reviews were more likely to provide this information than older reviews, but it highlights the importance of data and code sharing as recommended in the PRISMA guidelines.\textsuperscript{42}
When study level data was available, many effects were removed because the pooled sample size was small, or because there were fewer than ten studies on which to perform an Egger's test.
It seems that much of the current screen use research is small in scale, and there is a need for larger, high-quality studies.

@@

Screen use research has a well-established measurement problem, which impacts the individual studies of this umbrella review.
The vast majority of screen use research relies on self-reported data, which not only lacks the nuance required for understanding the effects of screen use, but may also be inaccurate.
In one systematic review on screen use and sleep,\textsuperscript{7} 66 of the 67 included studies used self-reported data for \emph{both} the exposure and outcome variable.
It has been established that self-reported screen use data has questionable validity.
In a meta-analysis of 47 studies comparing self-reported media use with logged measures, Parry et al\textsuperscript{43} found that the measures were only moderately correlated (\(r = 0.38\)), with self-reported problematic usage fairing worse (\(r = 0.25\)).
Indeed, of 622 studies which measured the screen use of 0---6 year-olds, only 69 provided any sort of psychometric properties for their measure, with only 19 studies reporting validity.\textsuperscript{44}
While some researchers have started using newer methods of capturing screen behaviours---such as wearable cameras\textsuperscript{45} or device-based loggers---\textsuperscript{46}these are still not widely adopted.
It may be that the field of screen use research cannot be sufficiently advanced until accurate, validated, and nuanced measures are more widely available and adopted.

@@

Our high-level approach limits the feasibility of examining fine-grained details of the individual studies.
For example, we did not examine moderators beyond age, nor did we rate the risk of bias for the individual studies.
Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment of quality (e.g., GRADE).\textsuperscript{47}
As such, we made decisions regarding the credibility of evidence, where others may have used different thresholds or metrics.
In addition, when faced with duplicate outcome/exposure combinations we chose to keep the one with the largest pooled sample size, assuming that this would capture the most comprehensive and most recent review.
Inspection of the excluded effect sizes suggests that this decision was not that impactful: our results would have been almost exactly the same has we used the number of included studies (\emph{k}) or the most recent review by publication year.
However, we provide the complete results in Supplementary Files 4 \& 5, along with the dataset (Supplementary File 6) for others to consider alternative criteria.

@@

We converted all effect sizes to a common metric (Pearson's r) to allow for comparisons of magnitude, but acknowledge that this assumes a linear relationship between the variables.
Some previous research suggests that associations are typically linear.\textsuperscript{18}
However, others have identified instances where non-linear relationships exist, especially for very high levels of screen use.\textsuperscript{17,48,49}
Additionally, our conversion may not always adequately account for differences in study design or measures of exposures and outcomes.
Care is needed, therefore, when interpreting the effect sizes.
In addition, reviews provide only historical evidence which may not keep up with the changing ways children can engage with screens.
While our synthesis of the existing evidence provides information about how screens might have influenced children in the past, it is difficult to know if these findings will translate to new forms of technology in the future.

@@

We prospectively registered our methods on the International Prospective Register of Systematic Reviews (PROSPERO; CRD42017076051) in October 2017.
We followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines.\textsuperscript{42}

@@

For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute's Quality Assessment of Systematic Reviews and Meta-Analyses tool\textsuperscript{50} (see Table 1).
We resolved disagreements by consensus, with a third researcher employed when needed.
We did not assess risk of bias in the individual studies that were included in each meta-analysis.

@@

To facilitate comparisons, we converted effect sizes to Pearson's \(r\) using established formulae.\textsuperscript{51,52}
Effect sizes on the original metric are provided in Supplementary File 6.
Throughout the results section we interpret the size of the effects using Funder and Ozer's guidelines:\textsuperscript{53} very small (0.05 \textless{} r \textless= 0.1), small (0.1 \textless{} r \textless= 0.2), medium (0.2 \textless{} r \textless= 0.2), large (0.3 \textless{} r \textless= 0.4), and very large (r \textgreater= 0.4).
These are similar to other interpretations based on empirical data.\textsuperscript{54}

@@

We descriptively present the remaining meta-analytic effect sizes.
To remove the differences in approach to meta-analyses across the reviews, we reran the effect size estimate using a random effects meta-analysis via the metafor package\textsuperscript{55} in R\textsuperscript{56} (version 4.3.0) when the meta-analysis's authors provided primary study data associated with these effects.
When required, we imputed missing sample sizes using mean imputation from the other studies within that review.
From our reanalysis we also extracted \(I^2\) values.
To test for publication bias, we conducted Egger's test\textsuperscript{57} when the number of studies within the review was ten or more,\textsuperscript{58} and conducted a test of excess significance.\textsuperscript{59}
We contacted authors who did not provide primary study data in their published article.
Where authors did not provide data in a format that could be re-analysed, we used the published results of their original meta-analysis.

@@

Statistical Credibility:
We employed a statistical classification approach to grade the credibility of the effect sizes in the literature.
To be considered `credible' an effect needed to be derived from a combined sample of \textgreater1,000 participants\textsuperscript{60} and have non-significant tests of publication bias (i.e., Egger's test and excess significance test).
We performed these analyses, and therefore the review needed to provide usable study-level data in order to be included.

@@

\emph{Figure 1: PRISMA Diagram.}

\emph{Figure 2: Education outcomes. Results for 22 unique effect sizes related to educational outcomes which met the criteria for statistical certainty. Findings are presented as correlations with both 95\% and 99.9\% confidence intervals.}

\emph{Figure 3: Health and health-related behaviour outcomes. Results for 21 unique effect sizes related to health and health-related behaviour outcomes which met the criteria for statistical certainty. Findings are presented as correlations with both 95\% and 99.9\% confidence intervals.}

@@

\leavevmode\vadjust pre{\hypertarget{ref-sadeghiradInfluenceUnhealthyFood2016}{}}%
\CSLLeftMargin{36. }
\CSLRightInline{Sadeghirad, B., Duhaney, T., Motaghipisheh, S., Campbell, N. R. C. \& Johnston, B. C. Influence of unhealthy food and beverage marketing on children's dietary intake and preference: A systematic review and meta-analysis of randomized trials. \emph{Obesity Reviews} \textbf{17}, 945--959 (2016).}

\leavevmode\vadjust pre{\hypertarget{ref-marshallRelationshipsMediaUse2004}{}}%
\CSLLeftMargin{37. }
\CSLRightInline{Marshall, S. J., Biddle, S. J. H., Gorely, T., Cameron, N. \& Murdey, I. Relationships between media use, body fatness and physical activity in children and youth: A meta-analysis. \emph{International Journal of Obesity} \textbf{28}, 1238--1246 (2004).}

\leavevmode\vadjust pre{\hypertarget{ref-elsonPolicyStatementsMedia2019}{}}%
\CSLLeftMargin{38. }
\CSLRightInline{Elson, M. \emph{et al.} Do policy statements on media effects faithfully represent the science? \emph{Advances in Methods and Practices in Psychological Science} \textbf{2}, 12--25 (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-ashtonScreenTimeChildren2019}{}}%
\CSLLeftMargin{39. }
\CSLRightInline{Ashton, J. J. \& Beattie, R. M. Screen time in children and adolescents: Is there evidence to guide parents and policy? \emph{The Lancet Child \& Adolescent Health} \textbf{3}, 292--294 (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-royalcollegeofpaediatricsandchildhealthHealthImpactsScreen2019}{}}%
\CSLLeftMargin{40. }
\CSLRightInline{Royal College of Paediatrics and Child Health. \emph{The health impacts of screen time: {A} guide for clinicians and parents.} (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-markerExploringMythChubby2022}{}}%
\CSLLeftMargin{41. }
\CSLRightInline{Marker, C., Gnambs, T. \& Appel, M. Exploring the myth of the chubby gamer: {A} meta-analysis on sedentary video gaming and body mass. \emph{Social Science \& Medicine} \textbf{301}, 112325 (2022).}

\leavevmode\vadjust pre{\hypertarget{ref-pagePRISMA2020Statement2020}{}}%
\CSLLeftMargin{42. }
\CSLRightInline{Page, M. J. \emph{et al.} \emph{The {PRISMA} 2020 statement: An updated guideline for reporting systematic reviews}. (2020) doi:\href{https://doi.org/10.31222/osf.io/v7gm2}{10.31222/osf.io/v7gm2}.}

\leavevmode\vadjust pre{\hypertarget{ref-parrySystematicReviewMetaanalysis2021}{}}%
\CSLLeftMargin{43. }
\CSLRightInline{Parry, D. A. \emph{et al.} A systematic review and meta-analysis of discrepancies between logged and self-reported digital media use. \emph{Nature Human Behaviour} \textbf{5}, 1535--1547 (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-byrneMeasurementScreenTime2021}{}}%
\CSLLeftMargin{44. }
\CSLRightInline{Byrne, R., Terranova, C. O. \& Trost, S. G. Measurement of screen time among young children aged 0\textendash 6 years: {A} systematic review. \emph{Obesity Reviews} \textbf{22}, (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-smithFeasibilityAutomatedCameras2019}{}}%
\CSLLeftMargin{45. }
\CSLRightInline{Smith, C., Galland, B. C., de Bruin, W. E. \& Taylor, R. W. Feasibility of automated cameras to measure screen use in adolescents. \emph{American journal of preventive medicine} \textbf{57}, 417--424 (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-rydingPassiveObjectiveMeasures2020}{}}%
\CSLLeftMargin{46. }
\CSLRightInline{Ryding, F. C. \& Kuss, D. J. Passive objective measures in the assessment of problematic smartphone use: {A} systematic review. \emph{Addictive Behaviors Reports} \textbf{11}, 100257 (2020).}

\leavevmode\vadjust pre{\hypertarget{ref-guyattGRADEGuidelinesIntroduction2011}{}}%
\CSLLeftMargin{47. }
\CSLRightInline{Guyatt, G. \emph{et al.} {GRADE} guidelines: 1. {Introduction}\textemdash{{GRADE}} evidence profiles and summary of findings tables. \emph{Journal of Clinical Epidemiology} \textbf{64}, 383--394 (2011).}

\leavevmode\vadjust pre{\hypertarget{ref-twengeMoreTimeTechnology2019}{}}%
\CSLLeftMargin{48. }
\CSLRightInline{Twenge, J. M. More {Time} on {Technology}, {Less Happiness}? {Associations Between Digital-Media Use} and {Psychological Well-Being}. \emph{Current Directions in Psychological Science} \textbf{28}, 372--379 (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-kellySocialMediaUse2018}{}}%
\CSLLeftMargin{49. }
\CSLRightInline{Kelly, Y., Zilanawala, A., Booker, C. \& Sacker, A. Social {Media Use} and {Adolescent Mental Health}: {Findings From} the {UK Millennium Cohort Study}. \emph{EClinicalMedicine} \textbf{6}, 59--68 (2018).}

\leavevmode\vadjust pre{\hypertarget{ref-NHLBIQualityAssessmentSystematic2014}{}}%
\CSLLeftMargin{50. }
\CSLRightInline{National Health, Lung, and Blood Institute. \emph{Quality {Assessment} of {Systematic Reviews} and {Meta-Analyses}}. (2014).}

\leavevmode\vadjust pre{\hypertarget{ref-bowmanEffectSizesStatistical2012}{}}%
\CSLLeftMargin{51. }
\CSLRightInline{Bowman, N. A. Effect {Sizes} and {Statistical Methods} for {Meta-Analysis} in {Higher Education}. \emph{Research in Higher Education} \textbf{53}, 375--382 (2012).}

\leavevmode\vadjust pre{\hypertarget{ref-jacobsEstimationBiserialCorrelation2017}{}}%
\CSLLeftMargin{52. }
\CSLRightInline{Jacobs, P. \& Viechtbauer, W. Estimation of the biserial correlation and its sampling variance for use in meta-analysis: {Biserial Correlation}. \emph{Research Synthesis Methods} \textbf{8}, 161--180 (2017).}

\leavevmode\vadjust pre{\hypertarget{ref-funderEvaluatingEffectSize2019}{}}%
\CSLLeftMargin{53. }
\CSLRightInline{Funder, D. C. \& Ozer, D. J. Evaluating {Effect Size} in {Psychological Research}: {Sense} and {Nonsense}. \emph{Advances in Methods and Practices in Psychological Science} \textbf{2}, 156--168 (2019).}

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{\newline\indent Word count: 5295}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

The most frequently reported exposures were physically active video games (\emph{n} = 31), general screen use (\emph{n} = 27), general TV programs and movies (\emph{n} = 20), and screen-based interventions to promote health (\emph{n} = 14).
Supplementary File 1 provides a list of all exposures identified.
The most frequently reported outcomes were body composition (\emph{n} = 30), general learning (\emph{n} = 24), depression (\emph{n} = 13), and general literacy (\emph{n} = 12).
Of the 273 unique exposure/outcome combinations, 241 occurred in only one review, with 23 appearing twice, and 9 appearing three or more times.
Full characteristics of the included studies are provided in Supplementary File 2.
After removing reviews with duplicate exposure/outcome combinations, our process yielded 253 unique effect/outcome combinations (retaining multiple effects for different age groups or study designs) contributed from 102 reviews.
These effects represent the findings of 2,451 primary studies, involving 1,937,501 participants.
The characteristics of the included effects are available in Supplementary File 3.

@@

We identified 164 unique outcome-exposure combinations associated with health or health-related behaviour outcomes.
We removed 40 effects that did not provide individual study-level data, 50 effects with samples \textless{} 1,000, and 53 effects with a significant Egger's test or insufficient studies to conduct the test.
No remaining studies had statistically significant tests for excess significance.
Effects not meeting one or more of these standards are presented in Supplementary File 5.
The remaining 21 meta-analytic associations met our criteria for credible evidence and are described below (see also Figure 3).
These 21 effects came from 15 meta-analytic reviews analysing data from 344 empirical studies with 859,562 individual participants.

@@

As an example, consider children watching television programs---an often cited form of screen use harm.
We found evidence for a small association with poorer academic performance and literacy skills for general television watching\textsuperscript{27}.
However, we also found evidence that if the content of the program was educational, or the child was watching the program with a parent (i.e., co-viewing), this exposure was instead associated with better literacy.\textsuperscript{28}
Thus, parents may play an important role in selecting content that is likely to benefit their children or, perhaps, interact with their children in ways that may foster literacy (e.g., asking their children questions about the program).
Similar nuanced findings were observed for video games.
The credible evidence we identified showed that video game playing was associated with poorer body composition and learning.\textsuperscript{27,29}
However, when the video game were designed specifically to teach numeracy, playing these games showed learning benefits.\textsuperscript{30}
One might expect that video games designed to be physically active could confer health benefits, but none of the meta-analyses examining this hypothesis met our thresholds for statistical credibility (see Supplementary Files 4 \& 5) therefore this hypothesis could not be addressed.

@@

Largely owing to a small number of studies or missing individual study data, there were few age-based conclusions that could be drawn from reviews which met our criteria for statistical certainty.
Given the differences in development across childhood and adolescence and the different ways children of various ages use screens, further examination of age-based differences is needed.
However, in the absence of this work, our study has shown how children are affected by screens in general.

@@

Our results have several implications for policy and practice.
Broadly, our findings align with the recommendations of others who suggest that current guidelines may be too simplistic, mischaracterise the strength of the evidence, or do not acknowledge the important nuances of the issue.\textsuperscript{36--38}
Our findings suggest that screen use is a complex issue, with associations based not just on duration and device type, but also on the content and the environment in which the exposure occurs.
Many current guidelines simplify this complex relationship as something that should be minimised.\textsuperscript{12,13}
We suggest that future guidelines need to embrace the complexity of the issue, to give parents and clinicians specific information to weigh the pros and cons of interactions with screens.

Given our results, we support the continuing trend of guidelines moving away from recommendations to reduce `screen use', and instead focusing on the type of screen use.
For example, we suggest that guidelines should discourage high levels of social media and internet use.
Guidelines may also consider adapting recommendations that promote the use of educational apps and video games, although these recommendations need to be balanced against the (very small) risks to adiposity.\textsuperscript{39}

Our results also have implications for future research.
Screen use research is extensive, varied, and rapidly growing.
Reviews tended to be general (e.g., all screen use) and even when more targeted (e.g., social media) nuances related to specific content (e.g., Instagram vs Facebook) have not been meta-analysed or have not produced credible evidence.
Fewer than 20\% of the effects identified met our criteria for statistical credibility.
Most studies which did not meet our criteria failed to provide study-level data (or did not provide sufficient data, such as including effect estimates but not sample sizes).
Newer reviews were more likely to provide this information than older reviews, but it highlights the importance of data and code sharing as recommended in the PRISMA guidelines.\textsuperscript{40}
When study level data was available, many effects were removed because the pooled sample size was small, or because there were fewer than ten studies on which to perform an Egger's test.
It seems that much of the current screen use research is small in scale, and there is a need for larger, high-quality studies.

@@

Screen use research has a well-established measurement problem, which impacts the individual studies of this umbrella review.
The vast majority of screen use research relies on self-reported data, which not only lacks the nuance required for understanding the effects of screen use, but may also be inaccurate.
In one systematic review on screen use and sleep,\textsuperscript{7} 66 of the 67 included studies used self-reported data for \emph{both} the exposure and outcome variable.
It has been established that self-reported screen use data has questionable validity.
In a meta-analysis of 47 studies comparing self-reported media use with logged measures, Parry et al\textsuperscript{41} found that the measures were only moderately correlated (\(r = 0.38\)), with self-reported problematic usage fairing worse (\(r = 0.25\)).
Indeed, of 622 studies which measured the screen use of 0---6 year-olds, only 69 provided any sort of psychometric properties for their measure, with only 19 studies reporting validity.\textsuperscript{42}
While some researchers have started using newer methods of capturing screen behaviours---such as wearable cameras\textsuperscript{43} or device-based loggers---\textsuperscript{44}these are still not widely adopted.
It may be that the field of screen use research cannot be sufficiently advanced until accurate, validated, and nuanced measures are more widely available and adopted.

@@

Our high-level approach limits the feasibility of examining fine-grained details of the individual studies.
For example, we did not examine moderators beyond age, nor did we rate the risk of bias for the individual studies.
Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment of quality (e.g., GRADE).\textsuperscript{45}
As such, we made decisions regarding the credibility of evidence, where others may have used different thresholds or metrics.
In addition, when faced with duplicate outcome/exposure combinations we chose to keep the one with the largest pooled sample size, assuming that this would capture the most comprehensive and most recent review.
Inspection of the excluded effect sizes suggests that this decision was not that impactful: our results would have been almost exactly the same has we used the number of included studies (\emph{k}) or the most recent review by publication year.
However, we provide the complete results in Supplementary Files 4 \& 5, along with the dataset (Supplementary File 6) for others to consider alternative criteria.

@@

We converted all effect sizes to a common metric (Pearson's r) to allow for comparisons of magnitude, but acknowledge that this assumes a linear relationship between the variables.
Some previous research suggests that associations are typically linear.\textsuperscript{18}
However, others have identified instances where non-linear relationships exist, especially for very high levels of screen use.\textsuperscript{17,46,47}
Additionally, our conversion may not always adequately account for differences in study design or measures of exposures and outcomes.
Care is needed, therefore, when interpreting the effect sizes.
In addition, reviews provide only historical evidence which may not keep up with the changing ways children can engage with screens.
While our synthesis of the existing evidence provides information about how screens might have influenced children in the past, it is difficult to know if these findings will translate to new forms of technology in the future.

@@

We prospectively registered our methods on the International Prospective Register of Systematic Reviews (PROSPERO; CRD42017076051) in October 2017.
We followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines.\textsuperscript{40}

@@

For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute's Quality Assessment of Systematic Reviews and Meta-Analyses tool\textsuperscript{48} (see Table 1).
We resolved disagreements by consensus, with a third researcher employed when needed.
We did not assess risk of bias in the individual studies that were included in each meta-analysis.

@@

To facilitate comparisons, we converted effect sizes to Pearson's \(r\) using established formulae.\textsuperscript{49,50}
Effect sizes on the original metric are provided in Supplementary File 6.
Throughout the results section we interpret the size of the effects using Funder and Ozer's guidelines:\textsuperscript{51} very small (0.05 \textless{} r \textless= 0.1), small (0.1 \textless{} r \textless= 0.2), medium (0.2 \textless{} r \textless= 0.2), large (0.3 \textless{} r \textless= 0.4), and very large (r \textgreater= 0.4).
These are similar to other interpretations based on empirical data.\textsuperscript{52}

@@

We descriptively present the remaining meta-analytic effect sizes.
To remove the differences in approach to meta-analyses across the reviews, we reran the effect size estimate using a random effects meta-analysis via the metafor package\textsuperscript{53} in R\textsuperscript{54} (version 4.3.0) when the meta-analysis's authors provided primary study data associated with these effects.
When required, we imputed missing sample sizes using mean imputation from the other studies within that review.
From our reanalysis we also extracted \(I^2\) values.
To test for publication bias, we conducted Egger's test\textsuperscript{55} when the number of studies within the review was ten or more,\textsuperscript{56} and conducted a test of excess significance.\textsuperscript{57}
We contacted authors who did not provide primary study data in their published article.
Where authors did not provide data in a format that could be re-analysed, we used the published results of their original meta-analysis.

@@

Statistical Credibility:
We employed a statistical classification approach to grade the credibility of the effect sizes in the literature.
To be considered `credible' an effect needed to be derived from a combined sample of \textgreater1,000 participants\textsuperscript{58} and have non-significant tests of publication bias (i.e., Egger's test and excess significance test).
We performed these analyses, and therefore the review needed to provide usable study-level data in order to be included.

@@

\emph{Figure 1: PRISMA flow diagram.}

\emph{Figure 2: Education outcomes. Forest plot for 22 unique effect sizes related to educational outcomes which met the criteria for statistical certainty. Findings are presented as correlations (two-sided) with both 95\% and 99.9\% confidence intervals.}

\emph{Figure 3: Health and health-related behaviour outcomes. Forest plot for 21 unique effect sizes related to health and health-related behaviour outcomes which met the criteria for statistical certainty. Findings are presented as correlations (two-sided) with both 95\% and 99.9\% confidence intervals.}

@@

\leavevmode\vadjust pre{\hypertarget{ref-elsonPolicyStatementsMedia2019}{}}%
\CSLLeftMargin{36. }
\CSLRightInline{Elson, M. \emph{et al.} Do policy statements on media effects faithfully represent the science? \emph{Advances in Methods and Practices in Psychological Science} \textbf{2}, 12--25 (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-ashtonScreenTimeChildren2019}{}}%
\CSLLeftMargin{37. }
\CSLRightInline{Ashton, J. J. \& Beattie, R. M. Screen time in children and adolescents: Is there evidence to guide parents and policy? \emph{The Lancet Child \& Adolescent Health} \textbf{3}, 292--294 (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-royalcollegeofpaediatricsandchildhealthHealthImpactsScreen2019}{}}%
\CSLLeftMargin{38. }
\CSLRightInline{Royal College of Paediatrics and Child Health. \emph{The health impacts of screen time: {A} guide for clinicians and parents.} (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-markerExploringMythChubby2022}{}}%
\CSLLeftMargin{39. }
\CSLRightInline{Marker, C., Gnambs, T. \& Appel, M. Exploring the myth of the chubby gamer: {A} meta-analysis on sedentary video gaming and body mass. \emph{Social Science \& Medicine} \textbf{301}, 112325 (2022).}

\leavevmode\vadjust pre{\hypertarget{ref-pagePRISMA2020Statement2020}{}}%
\CSLLeftMargin{40. }
\CSLRightInline{Page, M. J. \emph{et al.} \emph{The {PRISMA} 2020 statement: An updated guideline for reporting systematic reviews}. (2020) doi:\href{https://doi.org/10.31222/osf.io/v7gm2}{10.31222/osf.io/v7gm2}.}

\leavevmode\vadjust pre{\hypertarget{ref-parrySystematicReviewMetaanalysis2021}{}}%
\CSLLeftMargin{41. }
\CSLRightInline{Parry, D. A. \emph{et al.} A systematic review and meta-analysis of discrepancies between logged and self-reported digital media use. \emph{Nature Human Behaviour} \textbf{5}, 1535--1547 (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-byrneMeasurementScreenTime2021}{}}%
\CSLLeftMargin{42. }
\CSLRightInline{Byrne, R., Terranova, C. O. \& Trost, S. G. Measurement of screen time among young children aged 0\textendash 6 years: {A} systematic review. \emph{Obesity Reviews} \textbf{22}, (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-smithFeasibilityAutomatedCameras2019}{}}%
\CSLLeftMargin{43. }
\CSLRightInline{Smith, C., Galland, B. C., de Bruin, W. E. \& Taylor, R. W. Feasibility of automated cameras to measure screen use in adolescents. \emph{American journal of preventive medicine} \textbf{57}, 417--424 (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-rydingPassiveObjectiveMeasures2020}{}}%
\CSLLeftMargin{44. }
\CSLRightInline{Ryding, F. C. \& Kuss, D. J. Passive objective measures in the assessment of problematic smartphone use: {A} systematic review. \emph{Addictive Behaviors Reports} \textbf{11}, 100257 (2020).}

\leavevmode\vadjust pre{\hypertarget{ref-guyattGRADEGuidelinesIntroduction2011}{}}%
\CSLLeftMargin{45. }
\CSLRightInline{Guyatt, G. \emph{et al.} {GRADE} guidelines: 1. {Introduction}\textemdash{{GRADE}} evidence profiles and summary of findings tables. \emph{Journal of Clinical Epidemiology} \textbf{64}, 383--394 (2011).}

\leavevmode\vadjust pre{\hypertarget{ref-twengeMoreTimeTechnology2019}{}}%
\CSLLeftMargin{46. }
\CSLRightInline{Twenge, J. M. More {Time} on {Technology}, {Less Happiness}? {Associations Between Digital-Media Use} and {Psychological Well-Being}. \emph{Current Directions in Psychological Science} \textbf{28}, 372--379 (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-kellySocialMediaUse2018}{}}%
\CSLLeftMargin{47. }
\CSLRightInline{Kelly, Y., Zilanawala, A., Booker, C. \& Sacker, A. Social {Media Use} and {Adolescent Mental Health}: {Findings From} the {UK Millennium Cohort Study}. \emph{EClinicalMedicine} \textbf{6}, 59--68 (2018).}

\leavevmode\vadjust pre{\hypertarget{ref-NHLBIQualityAssessmentSystematic2014}{}}%
\CSLLeftMargin{48. }
\CSLRightInline{National Health, Lung, and Blood Institute. \emph{Quality {Assessment} of {Systematic Reviews} and {Meta-Analyses}}. (2014).}

\leavevmode\vadjust pre{\hypertarget{ref-bowmanEffectSizesStatistical2012}{}}%
\CSLLeftMargin{49. }
\CSLRightInline{Bowman, N. A. Effect {Sizes} and {Statistical Methods} for {Meta-Analysis} in {Higher Education}. \emph{Research in Higher Education} \textbf{53}, 375--382 (2012).}

\leavevmode\vadjust pre{\hypertarget{ref-jacobsEstimationBiserialCorrelation2017}{}}%
\CSLLeftMargin{50. }
\CSLRightInline{Jacobs, P. \& Viechtbauer, W. Estimation of the biserial correlation and its sampling variance for use in meta-analysis: {Biserial Correlation}. \emph{Research Synthesis Methods} \textbf{8}, 161--180 (2017).}

\leavevmode\vadjust pre{\hypertarget{ref-funderEvaluatingEffectSize2019}{}}%
\CSLLeftMargin{51. }
\CSLRightInline{Funder, D. C. \& Ozer, D. J. Evaluating {Effect Size} in {Psychological Research}: {Sense} and {Nonsense}. \emph{Advances in Methods and Practices in Psychological Science} \textbf{2}, 156--168 (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-gignacEffectSizeGuidelines2016}{}}%
\CSLLeftMargin{52. }
\CSLRightInline{Gignac, G. E. \& Szodorai, E. T. Effect size guidelines for individual differences researchers. \emph{Personality and Individual Differences} \textbf{102}, 74--78 (2016).}

\leavevmode\vadjust pre{\hypertarget{ref-R-metafor}{}}%
\CSLLeftMargin{53. }
\CSLRightInline{Viechtbauer, W. \emph{Metafor: Meta-analysis package for r}. (2023).}

\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
\CSLLeftMargin{54. }
\CSLRightInline{R Core Team. \emph{R: A language and environment for statistical computing}. (R Foundation for Statistical Computing, 2023).}

\leavevmode\vadjust pre{\hypertarget{ref-eggerBiasMetaanalysisDetected1997}{}}%
\CSLLeftMargin{55. }
\CSLRightInline{Egger, M., Smith, G. D., Schneider, M. \& Minder, C. Bias in meta-analysis detected by a simple, graphical test. \emph{BMJ} \textbf{315}, 629--634 (1997).}
